Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-03-10 docs/thesis/chap-related_work.tex
work on thesis

The Mathematics Information Retrieval Workshop\cite{mir_worksop} held in the context of the Conference of Intelligent Computer Mathematics in July 2012, was the first official event in the area of MIR. Here, a small competition was held to evaluate different systems and approaches.

@@

Other systems that provide similar search functionalities are \url{Uniquation} and \url{http://www.symbolab.com/}, however detailed information about the systems are not provided. Finally Wolfram Alpha\cite{wolframalpha} is a very powerful tool that allows to find information about lots of mathematical concepts and a wide variety of other objects (Even pokemons).

>>>>

The Mathematics Information Retrieval Workshop\cite{mir_workshop} held in the context of the Conference of Intelligent Computer Mathematics in July 2012, was the first official event in the area of MIR. Here, a small competition was held to evaluate different systems and approaches.

@@

Other systems that provide similar search functionalities are \url{Uniquation} and \url{http://www.symbolab.com/}, however detailed information about the systems are not provided. Finally Wolfram Alpha\cite{wolframalpha} is a very powerful tool that allows to find information about lots of mathematical concepts and a wide variety of other objects (Even Pokemon).
